Transfer report

### 2019-01-13 Report/final-results.Rmd
Updates final report

To investigate further, we conducted separate one-way ANOVAs to compare learning conditions for walked distance and visitation errors for the last block of learning (block 3). There were main effects of learning condition for both walked distance, `r apa_print(aov(min_norm_distance ~ learning.condition, only_blocks(sub_walk_all, 3)))$statistic`, and visitation errors, `r  apa_print(aov(errors ~ learning.condition, only_blocks(sub_walk_all, 3)))$statistic`). Comparing the conditions closer, we find that there is a significant difference in visitations error performance between real world and desktop learning (`r apa_print(t.test(errors ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Real', 'Desktop'), c(1,3))))$statistic`) and real world nad treadmill VR learning (`r apa_print(t.test(errors ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Real', 'Treadmill VR'), c(1,3))))$statistic`), but no difference between Desktop and Treadmill learning (`r apa_print(t.test(errors ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Desktop', 'Treadmill VR'), c(1,3))))$statistic`). The situation is the same for distance comparisons.

@@

@@

In the last testing block (block 6), we found no differences among the groups in either error rate (`r apa_print(aov(errors ~ learning.condition, only_blocks(sub_walk_all, 6)))$statistic`), nor pointing performance (`r apa_print(aov(abs_error ~ learning.condition, data = sub_sop_all[sub_sop_all$phase == 2,]))$statistic$learning_condition`). However we still see small difference in distance performance (`r apa_print(aov(min_norm_distance ~ learning.condition, only_blocks(sub_walk_all, 6)))$statistic`), with Treadmill VR group (`r m_sd_report(only_conditions_blocks(sub_walk_all, "Real", 6)$min_norm_distance)`) performing slightly worse than the real world learning group (`r m_sd_report(only_conditions_blocks(sub_walk_all, "Real", 6)$min_norm_distance)`), `r apa_print(t.test(min_norm_distance ~ learning.condition, only_conditions(sub_walk_all, c('Treadmill VR', 'Real'))))$statistic`.

@@

A different story is in comparing the visitation errors across conditions in the last block, where one-way ANOVA shows significant difference (`r apa_print(aov(min_norm_distance ~ condition, only_blocks(walk_all, c(6))))$statistic`) and Tukey's post hoc tests demonstrates significant differences between all conditions that differs in transfer phase modality, e.g. participants in the real world always perform better than participants on the treadmill VR. Looking at the table XXX, we can clearly see that conditions with transfer phase happening in VR, despite having comparable walked distance, have higher number of visitation errors. We think that this may have emerged from two different sources: firstly, it can point to higher difficulty in recognizing proper doors because of lesser visual accuracy in the VR, where all doors look similar unlike real doors which may demonstrate unique signs of wear or use. The second reason for the increased number of visitation errors in VR conditions can be explained by the lesser "social impact" of wrong choice. Whereas in the real conditions, participants had to actively inquire the experimenter, there was technically no penalty for "trying out" wrong door in the VR.

@@

Assessing the effects of trasfering from the real world to the Treadmill VR, we ran 2 (Learning condition: real vs treadmill VR) x 2 (block 3 vs blcok 4) ANOVA on data for distance walked and visitation errors. There was no effect of block `r apa_print(ez_fit_distance$aov)$statistic$learning_condition` nor learning condition (`r apa_print(ez_fit_distance$aov)$statistic$learning_condition`) on distance walked and we observed no interaction effects (`r apa_print(ez_fit_distance$aov)$statistic$learning_condition_exp_block_id`). But we found significant interaction effect between block and learning condition in visitation errors, `r apa_print(ez_fit_errors$aov)$statistic$learning_condition_exp_block_id`.

@@

>>>>

To investigate further, we conducted separate one-way ANOVAs to compare learning conditions for walked distance and visitation errors for the last block of learning (block 3). There were main effects of learning condition for both walked distance, `r apa_print(aov(min_norm_distance ~ learning.condition, only_blocks(sub_walk_all, 3)))$statistic`, and visitation errors, `r  apa_print(aov(errors ~ learning.condition, only_blocks(sub_walk_all, 3)))$statistic`). Comparing the conditions closer, we find that there is a significant difference in visitations error performance between real world and desktop learning (`r apa_print(t.test(errors ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Real', 'Desktop'), 3)))$statistic`) and real world nad treadmill VR learning (`r apa_print(t.test(errors ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Real', 'Treadmill VR'), 3)))$statistic`), but no difference between Desktop and Treadmill learning (`r apa_print(t.test(errors ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Desktop', 'Treadmill VR'), 3)))$statistic`). The situation is the same for distance comparisons. real world and desktop learning (`r apa_print(t.test(min_norm_distance ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Real', 'Desktop'), 3)))$statistic`) and real world nad treadmill VR learning (`r apa_print(t.test(min_norm_distance ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Real', 'Treadmill VR'), 3)))$statistic`), but no difference between Desktop and Treadmill learning (`r apa_print(t.test(min_norm_distance ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Desktop', 'Treadmill VR'), 3)))$statistic`).

@@

```{r}
# Pre transfer plot of normalised distances
make_graph(only_blocks(sub_walk_all, 1:3), "learning.condition", "min_norm_distance", "exp_block_id") + 
  ylab("Average normalised trial distance") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

make_graph(only_blocks(sub_walk_all, 1:3), "learning.condition", "errors", "exp_block_id") + 
  ylab("Average normalised trial distance") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F)

ggplot(point_data_1, aes(x = learning.condition, y = abs_error, fill = learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average pointing error in degrees after learning phase") + xlab("Learning condition") + 
  scale_fill_manual(values = estimote_pal, "Learning condition")  + guides(fill=F)

@@

In the last testing block (block 6), we found no differences among the groups in either error rate (`r apa_print(aov(errors ~ learning.condition, only_blocks(sub_walk_all, 6)))$statistic`), nor pointing performance (`r apa_print(aov(abs_error ~ learning.condition, data = sub_sop_all[sub_sop_all$phase == 2,]))$statistic$learning_condition`). However we still see small difference in distance performance (`r apa_print(aov(min_norm_distance ~ learning.condition, only_blocks(sub_walk_all, 6)))$statistic`), with real group (`r m_sd_report(only_conditions_blocks(sub_walk_all, "Real", 6)$min_norm_distance)`) performing better than Treadmill VR group (`r m_sd_report(only_conditions_blocks(sub_walk_all, "Treadmill VR", 6)$min_norm_distance)`)(`r apa_print(t.test(min_norm_distance ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Treadmill VR', 'Real'), 6)))$statistic`) and desktop group (`r m_sd_report(only_conditions_blocks(sub_walk_all, "Desktop", 6)$min_norm_distance)`)(`r apa_print(t.test(min_norm_distance ~ learning.condition, only_conditions_blocks(sub_walk_all, c('Real', 'Desktop'), 6)))$statistic`).

@@

A different story is in comparing the visitation errors across conditions in the last block, where one-way ANOVA shows significant difference (`r apa_print(aov(errors ~ condition, only_blocks(walk_all, c(6))))$statistic`) and Tukey's post hoc tests demonstrates significant differences between all conditions that differs in transfer phase modality, e.g. participants in the real world always perform better than participants on the treadmill VR. Looking at the table XXX, we can clearly see that conditions with transfer phase happening in VR, despite having comparable walked distance, have higher number of visitation errors. We think that this may have emerged from two different sources: firstly, it can point to higher difficulty in recognizing proper doors because of lesser visual accuracy in the VR, where all doors look similar unlike real doors which may demonstrate unique signs of wear or use. The second reason for the increased number of visitation errors in VR conditions can be explained by the lesser "social impact" of wrong choice. Whereas in the real conditions, participants had to actively inquire the experimenter, there was technically no penalty for "trying out" wrong door in the VR.

@@

Assessing the effects of trasfering from the real world to the Treadmill VR, we ran 2 (Learning condition: real vs treadmill VR) x 2 (block 3 vs blcok 4) ANOVA on data for distance walked and visitation errors. There was no effect of block `r apa_print(ez_fit_distance$aov)$statistic$exp_block_id` nor learning condition (`r apa_print(ez_fit_distance$aov)$statistic$learning_condition`) on distance walked and we observed no interaction effects (`r apa_print(ez_fit_distance$aov)$statistic$learning_condition_exp_block_id`). But we found significant interaction effect between block and learning condition in visitation errors, `r apa_print(ez_fit_errors$aov)$statistic$learning_condition_exp_block_id`.

@@

```{r}

walk_all_filtered <- rbind(sub_walk_all, sub_walk_all_2)
ggplot(only_blocks(walk_all_filtered, 6), aes(x = condition, y = min_norm_distance, fill = learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average path distance in the last block of the transfer phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal, "Condition")  + guides(fill=F)

ggplot(only_blocks(walk_all_filtered, 6), aes(x = condition, y = errors, fill = learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Number of visiting errors in the last block of the transfer phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal, "Condition")  + guides(fill=F)
```
